Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Created data table for supervised learning

@@

The following table directly compares performance of the semi-supervised learning systems, and also includes the neural network used in the original PICO-60 paper as a baseline.

>>>>

The following table compares the accuracy and mean class-wise standard deviation values of various supervised learning configurations:

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Optimal Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $DeepConv(\omega)$ & 77\% & X \\
    \hline
    $DeepConvWithPos(\omega, \chi)$ & 91\% & X \\
    \hline
\end{tabular}

@@

The following table directly compares performance of the semi-supervised learning systems, and also includes the neural network used in the original PICO-60 paper as a baseline:
